Nail: A practical interface generator for data formats

### 2014-04-02 paper/concl.tex
minor nits in the intro
some relwk nits; one XXX regarding hammer vs nail
conclusion

\section{Conclusion}

This paper presented the initial design and implementation of
\textit{Nail}, an XXX...

>>>>

\section{Conclusion}
\label{s:concl}

This paper presented the initial design and implementation of
\textit{Nail}, a parser generator that aims to minimize the amount
of programmer effort.  Nail achieves this by reducing the expressive
power of the grammar, maintaining a \emph{semantic bijection} between
data formats and internal representations, and allowing programmers to
specify \emph{structural dependencies} on the data format.  This avoids
the need for programmers to write explicit semantic actions for input
and output processing.  We hope that by reducing programmer effort
required to use a parser generator, Nail will enable more application
developers to use generated parsers in practice.  Our prototype source
code is available at \url{https://github.com/jbangert/nail}.

### 2014-04-02 paper/impl.tex
Conclusion, eval, future work
conclusion

The current prototype of the Nail parser generator supports the C programming
language and top down parsers. Options for C++ STL data models and emitting
Packrat parser~\cite{packrat-parsing:icfp02} are under heavy development. In
this section, we will discuss some particular features of our parser
implementation.

The source code of our implementation, together with the examples described in
\S\ref{s:eval} are available on GitHub\footnote{\url{https://github.com/jbangert/nail}}.
\paragraph{Parsing}
A generated Nail parser makes two passes through the input , the first to
validate and recognise the input, the second to bind this data to the internal
model. Currently the parser is a straightforward top down parser, although
facilities have been made to add Packrat parsing to achieve linear parsing
times.
\paragraph{Memory allocation}
Many security vulnerabilities can occur when heap allocations are done
improperly. Therefore, just like Hammer, Nail avoids using the heap as much as
possible, using a custom arena allocator and allocating only fixed size blocks
from the system malloc. However, Nail extends upon Hammers approach and uses two
arenas for each parsed input. One arena is used for intermediate results and is
freed(and zeroed) after parsing completes, whereas the other arena is used only
for allocating the result and has to be freed by the programmer.

>>>>

The current prototype of the Nail parser generator supports the C programming
language and top-down parsers. Options for C++ STL data models and emitting
Packrat parser~\cite{packrat-parsing:icfp02} are under development. In
this section, we will discuss some particular features of our parser
implementation.

The source code of our implementation, together with the examples described in
\S\ref{s:eval} are available on GitHub at \url{https://github.com/jbangert/nail}.

\paragraph{Parsing}
A generated Nail parser makes two passes through the input , the first to
validate and recognise the input, the second to bind this data to the internal
model. Currently the parser is a straightforward top down parser, although
facilities have been made to add Packrat parsing to achieve linear parsing
times.
\paragraph{Memory allocation}
Many security vulnerabilities can occur when heap allocations are done
improperly. Therefore, just like Hammer, Nail avoids using the heap as much as
possible, using a custom arena allocator and allocating only fixed size blocks
from the system malloc. However, Nail extends upon Hammers approach and uses two
arenas for each parsed input. One arena is used for intermediate results and is
freed(and zeroed) after parsing completes, whereas the other arena is used only
for allocating the result and has to be freed by the programmer.
